Poster figures

### 2025-02-27 analysis/poster_ncar/presentation_figures.Rmd
Improves delta

```{r extent-delta, fig.height=11.99/cm, fig.width=24.09/cm}

dif_hindcast <- hindcast_extent |> 
  copy() |> 
  _[order(time)] |> 
  _[, dif := c(NA, diff(aice)/diff(as.numeric(as.Date(time)))), by = .(model, forecast_time, member)] |> 
  _[, median_ci(dif), by = .(model, time = update(time, year = 2000))]

extent_daily |> 
  _[order(time)] |> 
  _[, dif := c(NA, diff(aice)/diff(as.numeric(as.Date(time)))), by = .(dataset)] |> 
  _[, median_ci(dif), by = .(dataset, time = update(time, year = 2000))] |> 
  _[dataset == which_dataset] |> 
  ggplot(aes(time, mid)) +
  geom_hline(yintercept = 0, color = "gray50", linewidth = 0.2) +
  geom_smooth(aes(group = dataset, color = dataset),
              span = 30/366, linewidth = 0.5, se = FALSE, n = 366)  +
  geom_smooth(data = dif_hindcast,
              aes(color = model), span = 30/366, linewidth = 0.5, se = FALSE, n = 366) +
  scale_x_datetime(NULL, date_breaks = "1 month", 
                   date_labels = "%b", expand = c(0, 0)) +
  scale_y_continuous(NULL, labels = \(x) labels_extent(x, units = "M km²/day")) +
  theme(legend.position = "inside", legend.position.inside = c(0.9, 0.9), 
        legend.direction = "vertical") +
  scale_color_models
```

>>>>

```{r extent-delta-compute, fig.height=11.99/cm, fig.width=24.09/cm}
dif_hindcast <- hindcast_extent |> 
  copy() |> 
  _[order(time)] |> 
  _[, dif := c(NA, diff(aice)/diff(as.numeric(as.Date(time)))), by = .(model, forecast_time, member)] |> 
  _[, median_ci(dif), by = .(model, time = update(time, year = 2000))]

dif_hindcast <- rbind(
  dif_hindcast |> 
    copy() |> 
    _[, time := update(time, year = 1999)],
  dif_hindcast,
  dif_hindcast |> 
    copy() |> 
    _[, time := update(time, year = 2001)]
)

dif_extent <- extent_daily |> 
  _[order(time)] |> 
  _[, dif := c(NA, diff(aice)/diff(as.numeric(as.Date(time)))), by = .(dataset)] |> 
  _[, median_ci(dif), by = .(dataset, time = update(time, year = 2000))] |> 
  _[dataset == which_dataset]

dif_extent <- rbind(
  dif_extent |> 
    copy() |> 
    _[, time := update(time, year = 1999)],
  dif_extent,
  dif_extent |> 
    copy() |> 
    _[, time := update(time, year = 2001)]
)
```

```{r extent-delta, fig.height=11.99/cm, fig.width=24.09/cm}
n = 366*3

dif_extent |> 
  ggplot(aes(time, mid)) +
  geom_hline(yintercept = 0, color = "gray50", linewidth = 0.2) +
  geom_smooth(aes(group = dataset, color = dataset), 
              method = "loess",
              span = 30/n, linewidth = 0.5, se = FALSE, n = n)  +
  # geom_line() +
  geom_smooth(data = dif_hindcast,
              method = "loess",
              aes(color = model), span = 30/n, linewidth = 0.5, se = FALSE, n = n) +
  scale_x_datetime(NULL, date_breaks = "1 month", 
                   date_labels = "%b", expand = c(0, 0)) +
  scale_y_continuous(NULL, labels = \(x) labels_extent(x, units = "M km²/day")) +
  theme(legend.position = "inside", legend.position.inside = c(0.9, 0.9), 
        legend.direction = "vertical") +
  scale_color_models +
  coord_cartesian(xlim = as.POSIXct(c("2000-01-01", "2000-12-31"), tz = "UTC"))
```
